---
title: "Product Pitch"
output: ioslides_presentation
date: "2025-01-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Optimized Product Pricing

If one was to sell a product or service based on a voluntary pricing scheme. Just like the books for the
data science specialization, products can be offered in a pay what you want model. Using this data, it is
possible to set a price point for a second edition that maximizes profit.

## Assmuptions

- The data will follow a Gamma Distribution
- The sample is an actual representative sample
- Those willing to pay more, will pay the lower price point

## Sample Data


```{r cars, echo = TRUE}
data <- rgamma(30, shape = 5, scale = 4)
summary(data)
```

## Slide with Plot

With an example distribution, the goal would be to maximize the price, multiplied by the percentage of sales
that one would attain at that price.

```{r pressure}
library(MASS)
fit <- fitdistr(data, "gamma")
hist(data, probability = TRUE, main = "Gamma Distribution Fit", xlab = "Value")
      curve(dgamma(x, shape = fit$estimate["shape"], rate = fit$estimate["rate"]), add = TRUE, col = "blue")
```

